correlationstuff

### 2024-02-01 corstuff.Rmd
made correlation stuff pretty for the meeting

## Demographic IVs - two linear regression models
```{r, echo=FALSE, results='asis'}
library(stargazer)

@@

## Linear regression where Mean value is the intercept
Same model with mean value as intercept.

@@

##  Kahan scale Alpha values 
Hierarchy - Egalitarianism scale alpha  =  0.70
Individualism - Communitarianism scale alpha= 0.52
Only Individualism scale alpha = 0.31 
Only Communitarianism scale alpha = 0.72

@@

## Alternative Kahan Scores with Mean across
```{r, echo=FALSE}

Kscalescores <- fascales %>%
  dplyr::select(!starts_with(("K_I")))%>%
  rowwise()%>%
  dplyr::mutate(Communitarianism_score = mean(c_across(K_SHARM:K_SPROTECT)))%>%
  dplyr::mutate(Egalitarianism_score = mean(c_across(K_HEQUAL:K_ERADEQ2)))%>%
  dplyr::select(!starts_with(c("K_I","K_S", "K_H", "K_E")))

@@

## Kahan scater plot from the CFA scores 
```{r, echo = FALSE}

@@

print.psych(ecopolall2.fa, sort = TRUE)

@@

# all lms after FA
```{r, echo=FALSE}
# 3 linear models - 1) lm with demographic variables except age and State
m1_demo <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban, data = fascale_scores)

@@

summary(m1_kahan)
# 4) lm with ecopolvars 
m1_allscales <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State+ Pdevelop + Ndevelop + KahanS + KahanH , data = fascale_scores)

summary(m1_allscales)

@@

summary(m1_ecopol)

@@

summary(m1_allscales2)

@@

# Correlation Eco-pol and alt Kahan(mean across)

@@

fascale_scores2cor <- fascale_scores2 %>%
  dplyr::select(Communitarianism_score, Egalitarianism_score, Pdevelop, Ndevelop)

@@

@@

# 3) lm with kahan 
m1_kahan2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State + Communitarianism_score + Egalitarianism_score , data = fascale_scores2)
# Print model summary
summary(m1_kahan2)
#plot(m1_kahan)

# 4) lm with ecopolvars 
m1_allscales2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State+ Pdevelop + Ndevelop + Communitarianism_score + Egalitarianism_score , data = fascale_scores2)
# Print model summary
summary(m1_allscales2)
#plot(m1_allscales)

@@

summary(m1_ecopol2)

@@

\newpage
```{r, echo=FALSE, results='asis'}
library(stargazer)

@@

# LMs with EFA Kahan factors

@@

summary(demoEFA)

# 2) lm with all demographic variables
demoEFA2<- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State, data = fascale_scores4)
summary(demoEFA2)

@@

summary(demoEFA3)

@@

#2.  Kahan scale EFA  
```{r, echo=FALSE}

@@

summary(KEFA)

# 2) lm with all demographic variables
KEFA2<- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State, data = fascale_scores5)
summary(KEFA2)

@@

summary(KEFA3)

@@

# 3) lm with kahan 
TM2_kahan <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age  + Communitarianism_score + Egalitarianism_score, data = TM2)

@@

# 4) lm with ecopolvars 
TM2_allscales <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + Pdevelop + Ndevelop + Communitarianism_score + Egalitarianism_score , data = TM2)

>>>>

# Demographic IVs - two linear regression models
```{r, echo=FALSE, results='asis'}
library(stargazer)

@@

# Linear regression where Mean value is the intercept
Same model with mean value as intercept.

@@

#  Kahan scale Alpha values 
Hierarchy - Egalitarianism scale alpha  =  0.70
Individualism - Communitarianism scale alpha= 0.52
Only Individualism scale alpha = 0.31 
Only Communitarianism scale alpha = 0.72

@@

```{r, echo=FALSE}
## Alternative Kahan Scores with Mean across
Kscalescores <- fascales %>%
  dplyr::select(!starts_with(("K_I")))%>%
  rowwise()%>%
  dplyr::mutate(Individualism_score = mean(c_across(K_SHARM:K_SPROTECT)))%>%
  dplyr::mutate(Hierarchy_score = mean(c_across(K_HEQUAL:K_ERADEQ2)))%>%
  dplyr::select(!starts_with(c("K_I","K_S", "K_H", "K_E")))

@@

@@

#print.psych(ecopolall2.fa, sort = TRUE)

@@

# all lms after FA

# 3 linear models - 1) lm with demographic variables except age and State
m1_demo <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban, data = fascale_scores)

@@

#summary(m1_kahan)
# 4) lm with ecopolvars 
m1_allscales <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State+ Pdevelop + Ndevelop + KahanS + KahanH , data = fascale_scores)

#summary(m1_allscales)

@@

#summary(m1_ecopol)

@@

#summary(m1_allscales2)

@@

\newpage
#Correlation table Eco-pol scale and Kahan CFA scores

fascale_scorescor <- fascale_scores %>%
  dplyr::select(KahanS, KahanH, Pdevelop, Ndevelop)

cor_kecopol1 <- cor(fascale_scorescor)

print(cor_kecopol1)

# Correlation Eco-pol and alt Kahan (mean across)

@@

fascale_scores2cor <- fascale_scores2 %>%
  dplyr::select(Individualism_score, Hierarchy_score, Pdevelop, Ndevelop)

@@

\newpage
# Scatter plot 1: mean across Kahan scale scores around medians

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

#scatter plot of Kahan scale scores around the median scores on Individualism and Hierarchy scales.

Kscalescores %>%
  ggplot(aes(Individualism_score, Hierarchy_score))+
  geom_count(aes(color = ..n.., size = ..n..))+
  guides(color = 'legend')+
  geom_hline(yintercept=2, colour="black", lwd=1)+
  geom_vline(xintercept=3, colour="black", lwd=1)+
  labs(x = " Communitarianism to Individualism", y = "Egalitarianism to Hierarchy")+
  ylim(1,5)+
  xlim(1,5)+
  theme_minimal()

# Scater plot 2:  Kahan CFA scores 
```{r, echo = FALSE}

@@

# 3) lm with kahan 
m1_kahan2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State + Individualism_score + Hierarchy_score , data = fascale_scores2)
# Print model summary
#summary(m1_kahan2)
#plot(m1_kahan)

# 4) lm with ecopolvars 
m1_allscales2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State+ Pdevelop + Ndevelop + Individualism_score + Hierarchy_score , data = fascale_scores2)
# Print model summary
#summary(m1_allscales2)
#plot(m1_allscales)

@@

#summary(m1_ecopol2)

@@

@@

\newpage
# LMs with EFA Kahan factors

@@

#summary(demoEFA)

# 2) lm with all demographic variables
demoEFA2<- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State, data = fascale_scores4)
#summary(demoEFA2)

@@

#summary(demoEFA3)

@@

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(demoEFA,demoEFA2, demoEFA3, 
          title = "Lms with CFA Kahan",
          type = "latex"
)
cat("\\endgroup")

# 2. EXTRA:: Kahan scale EFA  
```{r, echo=FALSE}

@@

#summary(KEFA)

# 2) lm with all demographic variables
KEFA2<- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State, data = fascale_scores5)
#summary(KEFA2)

@@

#summary(KEFA3)

@@

# 3) lm with kahan 
TM2_kahan <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age  + Individualism_score + Hierarchy_score, data = TM2)

@@

# 4) lm with ecopolvars 
TM2_allscales <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + Pdevelop + Ndevelop + Individualism_score + Hierarchy_score , data = TM2)
